Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-05-01 analysis/paper/paper.Rmd
Added last sightings graph to paper. Continue distributions.
Change cache

```{r Fig-AllSppFreq, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="blah blah about consistency in target species occurrence. Maybe something about new spp showing up?"}

@@

```{r Fig-SiteSurveyCompletion, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="Need to add caption.",warning=FALSE}

@@

```{r Fig-SurveyTiming1, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="The annual dates of the first and last survey have both varied by over a month across the years."}

@@

JOEL - I specified ncol = 3 in the facet command but my html doesn't update with it (I know the command itself works since I can see the zoom in the script)? Are you able to see it? and/or does it work in solving the space problem?
```{r Fig-SurveyTiming2, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap=""}

@@

```{r Fig-SurveyDates1, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="The first sighting of each species each year.", warning=FALSE}
print(plot_timing_1)
```

@@

#to do

>>>>

```{r Fig-AllSppFreq, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap="blah blah about consistency in target species occurrence. Maybe something about new spp showing up?"}

@@

```{r Fig-SiteSurveyCompletion, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap="Need to add caption.",warning=FALSE}

@@

```{r Fig-SurveyTiming1, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap="The annual dates of the first and last survey have both varied by over a month across the years."}

@@

JOEL - I specified ncol = 3 in the facet command but my html doesn't update with it (I know the command itself works since I can see the zoom in the script)? Are you able to see it? and/or does it work in solving the space problem?
```{r Fig-SurveyTiming2, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap=""}

@@

```{r Fig-SurveyDates1, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap="The first sighting of each species each year.", warning=FALSE}
print(plot_timing_1)
```

@@

```{r Fig-SurveyDates2, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap="The last sighting of each species each year.", warning=FALSE}
print(plot_timing_2)
```
